\documentclass[UKenglish]{template/ifimaster}
%\usepackage[latin1]{inputenc}
\usepackage[T1]{fontenc,url}
\urlstyle{sf}
\usepackage{xargs}
\usepackage{babel}
\usepackage{textcomp}
\usepackage{template/uiosloforside}
\usepackage{varioref}
\usepackage{graphicx}
\usepackage{color}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{tikz}
\usepackage{template/pgf-umlsd}
\usepackage{hyperref}
\usepackage{xspace}
\usepackage{subfigure}
\usepackage{minibox}
\usepackage{expl3}
\usepackage{times}
\usepackage{template/thesis}
\usepackage{template/mytikz}
\usepackage{minted}
\usepackage{framed}
\usepackage{latexsym}
\usepackage[numbers]{natbib}
\usepackage{setspace}
\usepackage{captcont}
\usepackage{pdfpages}
\usepackage{bibentry}
\usepackage[acronym,toc]{glossaries}
\usepackage{eurosym}
\usetikzlibrary{positioning,shapes,shadows,arrows,calc}

\makeglossaries
\input{acronyms}

\nobibliography*

\title{CloudML}
\subtitle{A DSL for model-based realization of applications in the cloud}
\author{Eirik Brandtzæg}
\date{Spring 2012}

\begin{document}
\uiosloforside[kind={Master thesis}]{}

\frontmatter{}
\maketitle{}
\onehalfspacing
%\doublespacing

%\chapter*{Abstract}
\begin{abstract}
  Cloud Computing offers a vast amount of resources,
  available for end users on a pay-as-you-go basis.
  The opportunity to choose between several cloud providers
  is alluded by complexity of cloud solution heterogeneity.
  Challenges with cloud deployment and resource provisioning
  are identified in this thesis through experiments,
  performing full cloud deployments with tools offered by cloud providers.
  To tackle these challenges a model-based language (named CloudML),
  is purposed to effectively tackle these challenges through abstraction.
  This language is supported by an engine able to provision nodes in \emph{``the cloud''}.
  Topologies for these nodes are defined through lexical templates.
  The engine supports $24$ cloud providers,
  through software reuse, by leveraging an existing library.
  Sufficient metadata for provisioned instances are provided through
  \emph{models@run.time} approach.
  The engine is implemented and experiments have been conducted towards
  provisioning on two of the major cloud providers, Amazon and Rackspace.
  These experiments are used to validate the effort of this thesis. 
  Perspectives and future visions of CloudML are expressed
  in the end of this thesis.
  This work is integrated as a part of the REMICS project.
\end{abstract}

\tableofcontents{}
\listoffigures{}
\listoftables{}

\chapter*{Preface}
%{\scriptsize
%\begin{minted}[]{brainfuck}
%>++++++++++[>+++++++>+++++++++++>+++++++++++>+++++++++++>++++++++++>+++++++++++
%+>++++++++++++>+++++++++++>++++++++++++>++++++++++>+++++>+++>+++++++>+++>++++++
%++++++>+++++++++++>++++++++++++>+++++++++++>++++++++++>+++>+++++++++++>++++++++
%+++>+++++++++++>++++++++++>+++>++++++++++++>+++++++++++>+++>++++++++++++>++++++
%++++>++++++++++>+++++++++++>+++++++++++>+++>++++++++>+++++++++++++++++++++++>++
%++++++++>++++++++++>++++++++++++>++++++++++++>+++++++++++>++++++++++>++++++++++
%+>+++>++++++++>+++++++++++>++++++++++++>++++++++++++>++++++++++>+++++++++++>+++
%>++++++++++>+++++++++++>+++++++++++>+++>++++++++++>+++++++++++>++++++++++++>+++
%>+++++++++++>+++++++++++>++++++++++++>++++++++++>+++++++++++>++++++++++>+++>+++
%+++++++>++++++++++>++++++++++>+++++++++++>++++++++++>++++++++++>++++++++++++>++
%+++++++++>+++++++++++>+++++++++++>+++>++++++++++++>+++++++++++>+++>++++++++++>+
%+++++++++++>++++++++++++>+++++++++++>++++++++++++>++++++++++++>+++>+++++++++++>
%++++++++++><<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<
%<<<<<<<<<<<<<<<<<<<<<<-]>+++>->++>++++>+>----->----->----->-->+>---->++>+++>++>
%->+>--->-->>++>-->----->--->+>++>---->+>++>---->++++>--->>--->++>+++>+++>-->---
%>----->---->----->+>>++>--->+>----->----->+>++++>++>++>+>++++>++>++++>----->---
%-->++>----->>----->--->>+>++>>+>>----->->--->---->----->+>>++>---->+>++>--->---
%-->----->----->----->---->++>->+><<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<
%<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<>.>.>.>.>.>.>.>.>.>.>.>.>.>.>.>.>.>
%.>.>.>.>.>.>.>.>.>.>.>.>.>.>.>.>.>.>.>.>.>.>.>.>.>.>.>.>.>.>.>.>.>.>.>.>.>.>.>.
%>.>.>.>.>.>.>.>.>.>.>.>.>.>.>.>.>.>.>.>.>.>.>.>.>.>.>.>.>.>.>.>.
%\end{minted}
%}

I would like to thank SINTEF, and my supervisor Arne J{\o}rgen Berre,
for providing me with this opportunity to dive into the world of Cloud Computing.
I also want to thank S{\'e}bastien Mosser for his immense amount of 
assistance through designing and implementing of CloudML.
And of course for his accommodation through the writing process of this thesis,
including repeated feedback.
The Scala community, Specs2 mailing list and \emph{jclouds} IRC channel have been of great assistance,
guiding and helping through the implementation of CloudML.

\mainmatter{}

\input{chapters/introduction}

\part{Context}

\input{chapters/background}
\input{chapters/state-of-the-art}
\input{chapters/challenges}
\input{chapters/requirements}

\part{Contribution}

\input{chapters/vision}
\input{chapters/design}
\input{chapters/implementation}
\input{chapters/validation}

\part{Conclusion}

\input{chapters/conclusions}
\input{chapters/perspectives}

\glsaddall
\printglossaries

\appendix
%% Removed because of Copyright issues
%% \chapter{First appendix - Towards CloudML}
%% \includepdf[pages=-]{pdfs/cloudmde.pdf}
%% \chapter{Second appendix - Cloud-Computing}
%% \includepdf[pages=-]{pdfs/benevol.pdf}

\backmatter{}
\bibliography{bibliography,seb}
\bibliographystyle{plainnat}
\end{document}
